
# Loading the data

```{r}
rm(list = ls()); gc()
library(readxl)
library(tidyverse)
library(moments)
library(igraph)

# Specify the folder
#data_location2 <- "C:/Users/mafekete/Dropbox/fungi/results_after_clearing/"

data_location2 <- "C:/Users/caaguila/OneDrive - Jyväskylän yliopisto/Documents - Fungal Networks and soil carbon/Poppy_seeds_experiments/camera images/processed data/results/"
```


Calling the data

```{r}
temp2 <- list.files(path = data_location2, pattern ="*-results.xlsx")
temp <- paste(data_location2, temp2, sep = "")
Edge_Traits <- lapply(temp,function(x){read_excel(x,sheet = "Edges")} )
Node_Traits <- lapply(temp,function(x){read_excel(x,sheet = "Nodes")} )
saveRDS(Edge_Traits, paste(data_location2, "Edge_Traits.RDS", sep = ""))
saveRDS(Node_Traits, paste(data_location2, "Node_Traits.RDS", sep = ""))


```
If they are already made above

```{r}
rm(list = ls()); gc()

library(readxl)
library(tidyverse)
library(moments)
library(igraph)

# Selected ones

#data_location2 <-  "C:/Users/mafekete/Dropbox/fungi/results_inoculation21022025_time1/"

temp2 <- list.files(path = data_location2, pattern ="*-results.xlsx")
temp <- paste(data_location2, temp2, sep = "")

Edge_Traits <- readRDS(paste(data_location2, "Edge_Traits.RDS", sep = ""))
Node_Traits <- readRDS(paste(data_location2, "Node_Traits.RDS", sep = ""))
```

Run in the console only!
```{r}
Node_Traits_c <-
  lapply(Node_Traits,function(prueba){
    
    prueba$min_angle<-apply(
      prueba[,c("node_Omin_Omaj","node_Omid_Omaj","node_Omin_Omid")],1,
      function(x){y<-min(x,na.rm=T)})
    
    prueba$min_angle[which(prueba$min_angle=="Inf")]<-NA
    prueba
  })

all(Node_Traits_c[[1]]$node_Strength==Node_Traits[[1]]$node_Strength)
Node_Traits<-Node_Traits_c;rm(Node_Traits_c)
#saveRDS(Node_Traits, paste(data_location2, "Node_Traits.RDS", sep = ""))
```

#Transforming it into igraph object


```{r}
#Transforming it into igraph object

colonies_ntwk <-
  
  mapply(function(x,z){
    y<-graph_from_edgelist(as.matrix(x[,c("EndNodes_1","EndNodes_2")]),directed = F)
    E(y)$name<-x$name
    E(y)$edge_id <- x$Name
    E(y)$weight<-x$Resistance_2ave
    E(y)$length<-x$Length
    E(y)$width<-x$Width
    E(y)$Volume <- x$Volume
    
    V(y)$Degrees<-degree(y)
    V(y)$Accessibility <- distances(y,v=as.numeric(V(y)[Degrees==max(V(y)$Degrees)])
                                  
                                  
    )
    V(y)$node_ID<-z$node_ID
    #V(y)$angle<-z$node_Omin_Omid
    V(y)$angle<-z$min_angle
    
    E(y)$type<-"Main"
    
    E(y)$e_distance<-(x$Length/x$Tortuosity)
    
    E(y)[incident(y,
                  as.numeric(V(y)[Degrees==max(V(y)$Degrees)])
    )]$type<-"Inoculum"
    
    y
  },Edge_Traits, Node_Traits, SIMPLIFY = F)


#saveRDS(Edge_Traits, paste(data_location2, "Edge_Traits.RDS", sep = "")); rm(Edge_Traits); gc()

# Spatial location
spatial.data <- lapply(Node_Traits,function(x){x[,c("node_ID","node_X_pix","node_Y_pix","name")]})

spatial.data <- lapply(spatial.data,function(l){as.matrix(l[,c(2,3)])})
spatial.data <- lapply(spatial.data,function(l){norm_coords(l, ymin=-1, ymax=1, xmin=-1, xmax=1)})

#Calculatig the MST

colonies_ntwk <-
lapply(colonies_ntwk,
       function(x){E(x)$weight[E(x)$type == "Inoculum"] <- 0
x})

Access_mst <-
  lapply(colonies_ntwk,
         mst)

```

Identifying which network traits belong to the MST and which ones do not


```{r}

colonies_ntwk <-
  
  mapply(function(g,ms_t){
    
      # Assign the attribute to the edges in the graph
    E(g)$in_mst <- (E(g)$edge_id%in%E(ms_t)$edge_id)
    g
    
  },colonies_ntwk, Access_mst, SIMPLIFY = F)

```



```{r}
saveRDS(Access_mst, paste(data_location2, "Access_mst.RDS", sep = ""))
#saveRDS(Node_Traits, paste(data_location2, "Node_Traits.RDS", sep = "")); rm(Node_Traits); gc()
saveRDS(spatial.data, paste(data_location2, "spatial.data.RDS", sep = "")); rm(spatial.data)
saveRDS(colonies_ntwk, paste(data_location2, "colonies_ntwk.RDS", sep = ""))
```


Calculating the summary values for each colony

Load in case they were done already

```{r, message=FALSE, warning=FALSE}
rm(list = ls());gc()

#data_location2 <- "C:/Users/mafekete/Dropbox/fungi/results_inoculation21022025_time1/"

temp2 <- list.files(path = data_location2, pattern ="*-results.xlsx")
temp <- paste(data_location2, temp2, sep = "")

colonies_ntwk <- readRDS(paste(data_location2, "colonies_ntwk.RDS", sep = ""))

Access_mst <- readRDS(paste(data_location2, "Access_mst.RDS", sep = ""))

```


```{r, message=FALSE, warning=FALSE}

#Calculating the summary values for each colony

colony_sum <- do.call("rbind",
                    
                    lapply(
                      colonies_ntwk,function(x){
                        
                        w<-data.frame(
                          name_col=unique(E(x)$name),
                          alpha_coeff=(ecount(x)-vcount(x)+1)/(2*vcount(x)-5),
                          beta_coeff=ecount(x)/vcount(x),
                          gamma_coeff=ecount(x)/(3*vcount(x)-6),
                          Root_eff=mean(1/V(x)[Accessibility>0]$Accessibility),
                          Reff_tip=mean(1/V(x)[Degrees==1&Accessibility>0]$Accessibility))
                        
                        y<-subgraph.edges(x,E(x)[type=="Main"])
                        
                        E(y)$hyphae<-"main"
                        E(y)[.inc(V(y)[Degrees==1])]$hyphae<-"tip"
                        
                        z <- data.frame(
                          name_col = unique(E(y)$name),
                          Hyphal_tip_length_median = 10^(mean(log10(E(y)[hyphae=="tip"&width>0]$length))),
                          Hyphal_main_length_median = 10^(mean(log10(E(y)[hyphae=="main"&width>0]$length))),
                          Hyphal_sec_length_median = 10^(mean(log10(E(y)[hyphae=="main"&width>0&in_mst==F]$length))),
                          
                          Hyphal_number_main = length(E(y)[hyphae == "main"]),
                          Hyphal_number_sec = length(E(y)[hyphae == "main"&in_mst==F]),
                          
                          Hyphal_number_tip = length(E(y)[hyphae == "tip"]),
                          
                          accessibility_skewness = skewness(V(y)[Degrees>1]$Accessibility),
                          
                          length_skewness_tip = skewness(E(y)[hyphae=="tip"&width>0]$length),
                          length_skewness_main = skewness(E(y)[hyphae=="main"&width>0]$length),
                          
                          volume_skewness_tip = skewness(E(y)[hyphae=="tip"&width>0]$Volume),
                          volume_skewness_main = skewness(E(y)[hyphae=="main"&width>0]$Volume),
                          
                          width_skewness_tip = skewness(E(y)[hyphae=="tip"&width>0]$width),
                          width_skewness_main = skewness(E(y)[hyphae=="main"&width>0]$width),
                          
                          Hyphal_tip_width_median = 10^(mean(log10(E(y)[hyphae=="tip"&width>0]$width))),
                          Hyphal_main_width_median = median(E(y)[hyphae=="main"&width>0]$width),#The unstransformed looks better
                          Hyphal_main_width_mean = mean(E(y)[hyphae=="main"&width>0]$width),
                          Hyphal_sec_width_mean = mean(E(y)[hyphae=="main"&width>0&in_mst==F]$width),#The unstransformed
                          
                          
                          Hyphal_tip_access = median(V(y)[Degrees==1]$Accessibility),
                          Hyphal_angle = median(V(y)[which(angle>0)]$angle),
                          
                          Mycelia_length = sum(E(y)$length),
                          Mycelia_Volume = sum(E(y)$Volume)
                          
                        )
                        
                        zw<-left_join(z,w)
                        zw
                        
                      })
)
```


```{r}
# Calculating global efficiency

library(parallel)
library(doParallel)

global_eff_no_start <-
  function(g){
    
    g <- subgraph(g, V(g)[Accessibility>0])
    
    get_eff <- function(i){return((1/(length(V(g)) - 1))*sum(1/distances(g, V(g)[i])[-i]))}
    no_cores <- detectCores() - 1 
    cl       <- makeCluster(no_cores)
    registerDoParallel(cl)  
    result <- foreach(i = seq_along(V(g)), .combine = c, .packages = "igraph") %dopar% get_eff(i)
    stopCluster(cl)
    rm(cl)
    Geff<-mean(result);Geff
  }

global_eff <-
  function(g){
    
    #g <- subgraph(g, V(g)[Accessibility>0])
    
    get_eff <- function(i){return((1/(length(V(g)) - 1))*sum(1/distances(g, V(g)[i])[-i]))}
    no_cores <- detectCores() - 1 
    cl       <- makeCluster(no_cores)
    registerDoParallel(cl)  
    result <- foreach(i = seq_along(V(g)), .combine = c, .packages = "igraph") %dopar% get_eff(i)
    stopCluster(cl)
    rm(cl)
    Geff<-mean(result);Geff
  }
```


```{r}

Real_summary_Geff2 <- sapply(colonies_ntwk, global_eff_no_start)
saveRDS(Real_summary_Geff2, paste(data_location2, "global_eff2.RDS", sep = ""))
```


```{r}

Real_summary_Geff2 <- readRDS(paste(data_location2, "global_eff2.RDS", sep = ""))

colony_sum$Geff_no_c <- Real_summary_Geff2
```

Calculating summary values for the Minimum spanning tree

```{r, message=FALSE, warning=FALSE}
# Calculating MST


#rm(colonies_ntwk); gc()

# Calculating summary values (hypal traits, coefficients and efficiencies ) for the minimum spanning trees (MST´s)
Access_mst_sum <-do.call("rbind",
                        lapply(
                          Access_mst,function(x){
                            
                            w<-data.frame(
                              name_col=unique(E(x)$name),
                              alpha_coeff=(ecount(x)-vcount(x)+1)/(2*vcount(x)-5),
                              beta_coeff=ecount(x)/vcount(x),
                              gamma_coeff=ecount(x)/(3*vcount(x)-6),
                              Root_eff=mean(1/V(x)[Accessibility>0]$Accessibility),
                              Reff_tip=mean(1/V(x)[Degrees==1&Accessibility>0]$Accessibility))
                            
                            y<-subgraph.edges(x,E(x)[type=="Main"])
                            
                            E(y)$hyphae<-"main"
                            E(y)[.inc(V(y)[Degrees==1])]$hyphae<-"tip"
                            
                            z<-data.frame(
                          name_col = unique(E(y)$name),
                          Hyphal_tip_length_median = 10^(mean(log10(E(y)[hyphae=="tip"&width>0]$length))),
                          Hyphal_main_length_median = 10^(mean(log10(E(y)[hyphae=="main"&width>0]$length))),
                          
                          Hyphal_number_main = length(E(y)[hyphae == "main"]),
                          Hyphal_number_tip = length(E(y)[hyphae == "tip"]),
                          
                          accessibility_skewness = skewness(V(y)[Degrees>1]$Accessibility),
                          
                          length_skewness_tip = skewness(E(y)[hyphae=="tip"&width>0]$length),
                          length_skewness_main = skewness(E(y)[hyphae=="main"&width>0]$length),
                          
                          volume_skewness_tip = skewness(E(y)[hyphae=="tip"&width>0]$Volume),
                          volume_skewness_main = skewness(E(y)[hyphae=="main"&width>0]$Volume),
                          
                          width_skewness_tip = skewness(E(y)[hyphae=="tip"&width>0]$width),
                          width_skewness_main = skewness(E(y)[hyphae=="main"&width>0]$width),
                          
                          Hyphal_tip_width_median = 10^(mean(log10(E(y)[hyphae=="tip"&width>0]$width))),
                          Hyphal_main_width_median = median(E(y)[hyphae=="main"&width>0]$width),#The unstransformed looks better
                          Hyphal_main_width_mean = mean(E(y)[hyphae=="main"&width>0]$width),#The unstransformed looks better
                          Hyphal_tip_access = median(V(y)[Degrees==1]$Accessibility),
                          Hyphal_angle = median(V(y)[which(angle>0)]$angle),
                              
                              Mycelia_length=sum(E(y)$length),
                              Mycelia_Volume=sum(E(y)$Volume)#,
                              
                            )
                            z<-left_join(z,w)
                            
                          })
)


```


```{r}
# Now the global efficieny of the MST


MST_summary_Geff2 <- sapply(Access_mst, global_eff_no_start)
saveRDS(MST_summary_Geff2, paste(data_location2, "global_MST_eff2.RDS", sep = ""))

###########

saveRDS(Access_mst, paste(data_location2, "Access_mst.RDS", sep = ""))
rm(Access_mst);gc()
```


```{r}


MST_summary_Geff2 <- readRDS(paste(data_location2, "global_MST_eff2.RDS", sep = ""))
Access_mst_sum$Geff_no_c <- MST_summary_Geff2

```


```{r}
# Summary_Tables
summary_Traits <- lapply(temp,function(x){read_excel(x,sheet = "Summary table")} )

summary_Traits_table_AZB <- bind_rows(summary_Traits)
summary_Traits_table_AZB$name_col <- temp
summary_Traits_table_AZB$name_col <- gsub(data_location2,"",summary_Traits_table_AZB$name_col)

summary_Traits_table_AZB$name_col <- gsub("\\-results\\.xlsx","",summary_Traits_table_AZB$name_col)

```


```{r}
### Biding the real and MST networks

colony_sum$Network<-"Real"
Access_mst_sum$Network<-"Resistance_MST"

all_data <- bind_rows(colony_sum,Access_mst_sum)

#all_data$Species <- str_extract(all_data$name_col, "Hf_|Rb_|Pv_|Pi_")

#adding this because there are some entries in Hf and Pv that have the word "shiny"

#all_data$name_col <- gsub("_shiny_", "_", all_data$name_col)

all_data <- left_join(all_data,
                    summary_Traits_table_AZB[,c("name_col","summary_mycelial_area",
                                                #"polygons_mean_polygon_Roughness",
                                                #"polygons_mean_polygon_Solidity",
                                                #"polygons_mean_polygon_Circularity",
                                                "summary_Geff","summary_Gnorm")])

#Then I can just calculated edge density for all (including the MSt´s)

all_data$Hyphal_density_tip <- all_data$Hyphal_number_tip/all_data$summary_mycelial_area
all_data$Hyphal_density_main <- all_data$Hyphal_number_main/all_data$summary_mycelial_area

#Changin the name of the area so it make more sense
names(all_data)[which(names(all_data)=="summary_mycelial_area")] <- "Mycelial_area"

### Scaling values from real networks by MST values

l <- length(all_data$name_col)

all_data_scaled <- all_data[c(1:(l/2)),]

all_data_scaled$Mycelia_length_MST <- all_data[c(1:(l/2)),]$Mycelia_length/all_data[c(((l/2)+1):l),]$Mycelia_length

all_data_scaled$Mycelia_Vol_MST <- all_data[c(1:(l/2)),]$Mycelia_Volume/all_data[c(((l/2)+1):l),]$Mycelia_Volume

#all_data_scaled$alpha_coeff_scaled<-all_data[c(1:32),]$alpha_coeff/all_data[c(33:64),]$alpha_coeff
#all_data_scaled$beta_coeff_scaled<-all_data[c(1:32),]$beta_coeff/all_data[c(33:64),]$beta_coeff
all_data_scaled$Root_eff_l_scaled<-all_data[c(1:(l/2)),]$Root_eff/sqrt(all_data[c(1:(l/2)),]$Mycelial_area)
all_data_scaled$Reff_tip_l_scaled<-all_data[c(1:(l/2)),]$Reff_tip/sqrt(all_data[c(1:(l/2)),]$Mycelial_area)
#all_data_scaled$Geff_MST<-all_data[c(1:(l/2)),]$Geff/all_data[c(((l/2)+1):l),]$Geff
all_data_scaled$Geff_MST<-all_data[c(1:(l/2)),]$summary_Geff/all_data[c(((l/2)+1):l),]$summary_Geff

#all_data_scaled$Geff_MST_no_c <- all_data[c(1:(l/2)),]$Geff_no_c/all_data[c(((l/2)+1):l),]$Geff_no_c

#all_data_scaled$phylum <- "Basidiomycota"
```


```{r}
saveRDS(all_data_scaled, paste(data_location2, "all_data_scaled.RDS", sep = ""))
saveRDS(all_data, paste(data_location2, "all_data.RDS", sep = ""))
#saveRDS(robustness, paste(data_location2, "robustness.RDS", sep = ""))
saveRDS(summary_Traits_table_AZB, paste(data_location2, "summary_Traits_table_AZB.RDS", sep = ""))
```


###### Robustness measures

```{r}
#data_location2 <- "C:/Users/mafekete/Dropbox/fungi/results_inoculation21022025_time1/"

temp2 <- list.files(path = data_location2, pattern ="*-results.xlsx")
temp <- paste(data_location2, temp2, sep = "")
```


```{r}
library(DescTools)
library(readxl)
library(tidyverse)

cv <- function(x){sd(x)/mean(x)}
```


Check whether this is necessary: 

In the old code this was necessary. Weird that not anymore
robustness$asc_width_robustness[which(is.na(robustness$asc_width_robustness))] <- 99
which(is.na(ordered_AUC$Fifty_mark_adj_Width_asc))

```{r}
######################################## Random Robustness ##########################################

cv <- function(x){sd(x)/mean(x)}

Random_robustness <- lapply(temp,function(x){read_excel(x,sheet = "Random Robustness")})

Random_AUC <- 
  bind_rows(lapply(Random_robustness,
                                   function(x){
                                     y <- split(x,as.factor(x$rep))
                                     bind_rows(lapply(y,function(y){
                                       data.frame(
                                         name = unique(y$name),
                                         rep = unique(y$rep),
                                         AUC = AUC(
                                           y$removed_percent,
                                           y$connected_percent,
                                           to = 95),
                                         AUC_adj =AUC(
                                           y$removed_percent,
                                           y$robustness,
                                           to = 95),
                                         Fifty_mark = approx(y$removed_percent, y$connected_percent)$x[
                                           which.min(abs(approx(y$removed_percent, y$connected_percent)$y-50))],
                                         
                                         Fifty_mark_adj = approx(y$removed_percent, y$robustness)$x[
                                           which.min(abs(approx(y$removed_percent, y$robustness)$y-50))]
                                                                                  )
                                       }))
                                   })) %>% 
  group_by(name) %>% 
  summarise_at(c("AUC","AUC_adj", "Fifty_mark", "Fifty_mark_adj"),
               list(mean = mean, cv =cv))

Random_AUC$name <- gsub("_shiny_", "_", Random_AUC$name)
saveRDS(Random_AUC, paste(data_location2,"Random_AUC.RDS", sep = ""))

#########################################  Spatial Robustness #######################################################
Spatial_robustness <- lapply(temp,function(x){read_excel(x,sheet = "Spatial Robustness")})

Spatial_AUC <- 
  bind_rows(lapply(Spatial_robustness,
                                  function(x){
                                    y <- split(x,as.factor(x$rep))
                                    bind_rows(lapply(y,function(y){
                                      data.frame(
                                        name = unique(y$name),
                                        rep = unique(y$rep),
                                        AUC = AUC(
                                          y$removed_percent,
                                          y$connected_percent,
                                          to = 95),
                                        AUC_adj =AUC(
                                          y$removed_percent,
                                          y$robustness,
                                          to = 95),
                                        Fifty_mark = approx(y$removed_percent, y$connected_percent)$x[
                                          which.min(abs(approx(y$removed_percent, y$connected_percent)$y-50))],
                                        
                                        Fifty_mark_adj = approx(y$removed_percent, y$robustness)$x[
                                          which.min(abs(approx(y$removed_percent, y$robustness)$y-50))]
                                      )
                                    }))
                                  })) %>% 
  group_by(name) %>% 
  summarise_at(c("AUC","AUC_adj", "Fifty_mark", "Fifty_mark_adj"),
               list(mean = mean, cv =cv))

Spatial_AUC$name <- gsub("_shiny_", "_", Spatial_AUC$name)

saveRDS(Spatial_AUC, paste(data_location2, "Spatial_AUC.RDS", sep = ""))

############################### Ordered Robustness #################################################
Ordered_robustness <- lapply(temp,function(x){read_excel(x,sheet = "Ordered Robustness")})

ordered_AUC <- 
  bind_rows(lapply(Ordered_robustness,
                                   function(x){
                                     y <- split(x,as.factor(paste(x$method, x$direction)))
                                     bind_rows(lapply(y,function(y){
                                       data.frame(
                                         name = unique(y$name),
                                       method = unique(y$method),
                                         direction = unique(y$direction),
                                       AUC = AUC(
                                         y$removed_percent,
                                         y$connected_percent,
                                         to = 95),
                                         AUC_adj =AUC(
                                           y$removed_percent,
                                           y$robustness,
                                           to = 95),
                                       Fifty_mark = approx(y$removed_percent, y$connected_percent)$x[
                                         which.min(abs(approx(y$removed_percent, y$connected_percent)$y-50))],
                                       
                                       Fifty_mark_adj = approx(y$removed_percent, y$robustness)$x[
                                         which.min(abs(approx(y$removed_percent, y$robustness)$y-50))]
                                       )
                                     }))
                                   })) %>% 
  pivot_wider(values_from = c(AUC, AUC_adj, Fifty_mark, Fifty_mark_adj), names_from = c(method, direction))

ordered_AUC$name <- gsub("_shiny_", "_", ordered_AUC$name)
saveRDS(ordered_AUC, paste(data_location2, "ordered_AUC.RDS", sep = ""))


```

Merging all data to be analyzed into one dataframe

```{r}

library(tidyverse)
library(readxl)
library(tidytext)
library(vegan)
library(ranger)
#data_location2 <- "C:/Users/mafekete/Dropbox/fungi/results_inoculation21022025_time1/"

#location <- "C:/Users/mafekete/Dropbox/fungi/"

# All methods deliver similar results, however after comparing them all visually and in pca the best ones were



# --------------- Loading data Hypholoma -----------------------------------

#folder <- "results_inoculation21022025_time1//"

Hf_T2_SF <- readRDS(paste(data_location2,"all_data_scaled.RDS", sep = ""))

Hf_T2_SF_mst <- readRDS(paste(data_location2,"all_data.RDS", sep = ""))
Hf_T2_SF_mst <- Hf_T2_SF_mst[which(Hf_T2_SF_mst$Network == "Resistance_MST"),
                             c("name_col", "summary_Geff",
                               "Geff_no_c",
                               "Root_eff",                         
                               "Reff_tip",
                               "accessibility_skewness",           
                               "length_skewness_tip",               "length_skewness_main",             
                               "volume_skewness_tip",               "volume_skewness_main",             
                               "width_skewness_tip",                "width_skewness_main",              
                               "Hyphal_tip_width_median",           "Hyphal_main_width_median",         
                               "Hyphal_main_width_mean", "Hyphal_main_length_median",
                               "Hyphal_tip_length_median")]
names(Hf_T2_SF_mst)[-1]  <- paste(names(Hf_T2_SF_mst)[-1], "_of_MST", sep = "")

Hf_T2_SF <- left_join(Hf_T2_SF, Hf_T2_SF_mst)

# adding new "colony" data also stored in the folder
temp = list.files(path = paste(data_location2, sep = ""), pattern = "*-results.xlsx")
temp <- paste(data_location2, temp,sep = "")

# For this I need to specify that the data is contained int an excel sheet called
# "Graph"
colony <- bind_rows(
  lapply(temp,function(x){read_excel(x,sheet = "Graph")} )); names(colony)[1] <- "name_col"

colony <- unique(colony[, c("name_col", "colony_Circularity")])
colony$name_col <- gsub("_shiny_", "_", colony$name_col)
Hf_T2_SF <- left_join(Hf_T2_SF, colony)

# Adding the new AUC measures
Carlos_random_rob <- readRDS(paste(data_location2,"Random_AUC.RDS", sep = ""))
names(Carlos_random_rob)[-1] <- paste("random_", names(Carlos_random_rob)[-1], sep = "")
names(Carlos_random_rob)[1]  <- "name_col"

Carlos_spatial_rob <- readRDS(paste(data_location2,"Spatial_AUC.RDS", sep = ""))
names(Carlos_spatial_rob)[-1] <- paste("spatial_", names(Carlos_random_rob)[-1], sep = "")
names(Carlos_spatial_rob)[1]  <- "name_col"

Carlos_ordered_rob <- readRDS(paste(data_location2,"ordered_AUC.RDS", sep = ""))
names(Carlos_ordered_rob)[1]  <- "name_col"

Carlos_rob <- 
  left_join(left_join(Carlos_ordered_rob, Carlos_spatial_rob),
            Carlos_random_rob)

#names(Carlos_rob)[-1] <- paste("CA_", names(Carlos_rob)[-1], sep = "")

Hf_T2_SF <- left_join(Hf_T2_SF,
                      Carlos_rob); rm(Carlos_rob, Carlos_ordered_rob, Carlos_spatial_rob, Carlos_random_rob)

#Hf_T2_SF$set_up <- gsub("Hf DD2//|//results//|processed data ", "", folder)


# ------------------------------------------------------------------------------------------

# on top the densities and the widht, angle and AUC
library(vegan)
library(tidyverse)

all_data_scaled_c <- Hf_T2_SF



all_data_scaled_c$Root_eff_a_scaled <- all_data_scaled_c$Root_eff/all_data_scaled_c$Mycelial_area
all_data_scaled_c$Reff_tip_a_scaled <- all_data_scaled_c$Reff_tip/all_data_scaled_c$Mycelial_area


all_data_scaled_c$Geff_MST_no_c <- all_data_scaled_c$Geff_no_c/all_data_scaled_c$Geff_no_c_of_MST
all_data_scaled_a <- all_data_scaled_c

saveRDS(all_data_scaled_a, paste(data_location2, "all_data_scaled_a.RDS", sep = ""))

```

